Compilation with Dynamic Grammars

### 2017-04-17 papers/paper.tex
Adds minor edits to 2nd draft of paper

\textbf{EDITING POINT}

@@

Glossa's support for the different versions of Python and C++ output are significantly developed, supporting 80-90\% of the syntax for each language. 
Glossa's support for FORTRAN is more experimental, but 100\% support would be trivial to add, since FORTRAN has very simple syntax.
Glossa could currently support more complex input languages, like C++ or Haskell, but the description files would be more difficult to write.

@@

Glossa has accomplished far more than it originally set out to: Perhaps the software will mature in the future, and eventually be used at the industry level.

>>>>

@@

Glossa's support for the different versions of Python and C++ output are significantly developed, supporting 80-90\% of the syntax for each language. 
However, support for FORTRAN is more experimental, but 100\% support would be trivial to add, since FORTRAN has very simple syntax.
Glossa could currently support more complex input languages, like C++ or Haskell, but the description files would be more difficult to write.

@@

However, Glossa in its current form is not intended to be industrial-level software. 
Instead, it is an investigation into creating a generalized compilation system that does not hardcore any rules. 
While Glossa is useful at doing \textit{some} automated translations, it is likely more useful for implementing new programming languages.
Because of the generalizations (discarding of hard-coded rules) that Glossa makes, changing language definitions is trivial compared to the difficulty of modifying the source of a compiler.

Glossa has accomplished far more than it originally set out to: Perhaps Glossa can be used as groundwork for an industrial-level compiler framework.
